There are several numbers of inventory apps commercially available for use. Different people have built the apps in different ways. Some apps perform really well whereas some other apps are not as promising as it looks.There are several apps that I looked at. one of the very first app that I looked at was \textbf{Inventory+ from Mostafa Ashour, Tryvin}. This app was priced at 4.99 dollars but it failed to implement even very basic features like bar code scan support, easy removal and addition of the item. Similarly another app that I looked on was \textbf{Inventory Control with Scanner by Starkode Limited Company}. As I researched I found the app to be slow and very buggy. Looking at the reviews lots of users were complaining about the app often crashing.\textbf{ Cashier by cashier live} was another app that i researched about. It is an inventory app integrated with the POS system. The app cost was $75$ per month. I tried out one of my friends copy but the app was very laggy. It was slow and creating a user feature was not working at that particular time. \textbf{myStock Inventory Manager by Trace Width Technology Solutions LLC.} is another app that I tried. This time the app was not reliable. It had trouble loading the items. Sync between two device is really poor. Similarly another app I used was \textbf{Inventory app - Zoho by zoho corporation}. The app was completely functional and it the one app that i like the most. \\
All these apps provide the basic functionality of storing and retriving information. Most of the apps are paid applications. These type of app does not work for our client because non of these apps store the location of the item. Upon entry non of the apps will ask for the preferred location for storage nor it provides the items location on retrieval. Also most of the apps are slow and unreliable. We want to provide something robust and easy to use to our customer.